Generate data for NOBA cod ensemble modeling

### 2020-03-27 NOBAcod.Rmd
cant push after 2FA update
stashing this here

```
d.name <- here("atlantisoutput","NOBA_march_2020")
functional.groups.file <- "nordic_groups_v04.csv"
biomass.pools.file <- "nordic_biol_v23.nc"
biol.prm.file <- "nordic_biol_incl_harv_v_007_3.prm"
box.file <- "Nordic02.bgm"
initial.conditions.file <- "nordic_biol_v23.nc"
run.prm.file <- "nordic_run_v01.xml"
scenario.name <- "nordic_runresults_01"
bioind.file <- "outputnordic_runresults_01BiomIndx.txt"
catch.file <- "outputnordic_runresults_01Catch.txt"
```

@@

```
#survey species inherited from omlist_ss
survspp <- omlist_ss$species_ss
# survey season and other time dimensioning parameters
# generalized timesteps all models
noutsteps <- omlist_ss$runpar$tstop/omlist_ss$runpar$outputstep
timeall <- c(0:noutsteps)
stepperyr <- if(omlist_ss$runpar$outputstepunit=="days") 365/omlist_ss$runpar$toutinc
midptyr <- round(median(seq(0,stepperyr)))

# model areas, subset in surveyconfig
allboxes <- c(0:(omlist_ss$boxpars$nbox - 1))

# fishery output: learned the hard way this can be different from ecosystem outputs
fstepperyr <- if(omlist_ss$runpar$outputstepunit=="days") 365/omlist_ss$runpar$toutfinc

# survey selectivity (agecl based)
# should return all age classes fully sampled (Atlantis output is 10 age groups per spp)
n_age_classes <- omlist_ss$funct.group_ss$NumCohorts
age_classes <- 1:n_age_classes

n_annages <- n_age_classes * omlist_ss$funct.group_ss$NumAgeClassSize
annages <- 1:n_annages

@@

```
# Default survey configuration here is a census
# Need to define survey season, area, efficiency, selectivity

#Atlantis model timestep corresponding to the true output--now from census_spec.R
timestep <- stepperyr #5

#Which atlantis timestep does the survey run in?--now from census_spec.R
# with 5 output steps per year, 0 is Jan-Feb-midMar, 1 is midMar-Apr-May, 
# 2 is June-July-midAug, 3 is midAug-Sept-Oct, 4 is Nov-Dec (ish)

survey_sample_time <- midptyr #2; defined in omdimensions.R

#The last timestep to sample
total_sample <- noutsteps-1 #495

#Vector of indices of survey times to pull
survey_sample_full <- seq(survey_sample_time,
                          total_sample, by=timestep)

survtime <- survey_sample_full

# survey area
# should return all model areas
survboxes <- allboxes

# survey efficiency (q)
# should return a perfectly efficient survey 
surveffic <- data.frame(species=survspp,
                     efficiency=rep(0.5,length(survspp)))

# survey selectivity (agecl based)
# this is by age class, need to change to use with ANNAGEBIO output
survselex <- data.frame(species=rep(survspp, each=n_age_classes),
                     agecl=rep(c(1:n_age_classes),length(survspp)),
                     selex=rep(1.0,length(survspp)*n_age_classes))

# WARNING!! comment above and use this for annage output
survselex <- data.frame(species=rep(survspp, each=n_annages),
                        agecl=rep(c(1:n_annages),length(survspp)),
                        selex=rep(1.0,length(survspp)*n_annages))

# effective sample size needed for sample_fish
# this effective N is high but not equal to total for numerous groups
surveffN <- data.frame(species=survspp, effN=rep(1000, length(survspp)))

# survey index cv needed for sample_survey_xxx
# cv = 0.1
surv_cv <- data.frame(species=survspp, cv=rep(0.1,length(survspp)))

# length at age cv for input into calc_age2length function
# function designed to take one cv for all species, need to change to pass it a vector
lenage_cv <- 0.1

# max size bin for length estimation, function defaults to 150 cm if not supplied
maxbin <- 150

@@

```
# Default fishery configuration here is a census
# Inherits species from input omlist_ss
fishspp <- omlist_ss$species_ss

#Number of years of data to pull
nyears <- 50

#Atlantis initialization period in years
burnin <- 30

# same time dimensioning parameters as in surveycensus.R
#Vector of indices of catch in numbers to pull (by timestep to sum)
fish_sample_full <- c(0:total_sample)  #total_sample defined in sardinesurvey.R
fish_burnin <- burnin*fstepperyr+1
fish_nyears <- nyears*fstepperyr
fish_times <- fish_sample_full[fish_burnin:(fish_burnin+fish_nyears-1)]
fish_timesteps <- seq(fish_times[5], max(fish_times), by=fstepperyr) #last timestep
#fish_years <- unique(floor(fish_times/fstepperyr)+1) # my original
fish_years <- unique(floor(fish_times/fstepperyr)) #from Christine's new sardine_config.R

fishtime <- fish_times

# fishery output: learned the hard way this can be different from ecosystem outputs
fstepperyr <- if(omlist_ss$runpar$outputstepunit=="days") 365/omlist_ss$runpar$toutfinc

# fishery sampling area
# should return all model areas, this assumes you see everything that it caught
fishboxes <- c(0:(omlist_ss$boxpars$nbox - 1))

# effective sample size needed for sample_fish
# this effective N is high but not equal to total for numerous groups
fisheffN <- data.frame(species=survspp, effN=rep(1000, length(survspp)))

#this adjusts for subannual fishery output so original effN is for whole year
fisheffN$effN <- fisheffN$effN/fstepperyr

# fishery catch cv can be used in sample_survey_biomass
# perfect observation
fish_cv <- data.frame(species=survspp, cv=rep(0.01,length(survspp)))
```

@@

@@

>>>>

```{r, code = readLines("NOBA2Config.R")}
```

@@

```{r, code = readLines("omdimensions.R")}
```

@@

```{r, code = readLines("codsurvey.R")}
```

@@

```{r, code = readLines("codfishery.R")}
```

@@

#### Survey weight at age (age classes)

```{r wtageclass-1}

wtage <- readRDS(file.path(d.name, paste0(scenario.name, "survObsWtAtAge.rds")))
wtage <- wtage[[1]]

wageplot <- ggplot(wtage, aes(time, wtage)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (5 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " annual mid year sample"))

wageplot + facet_wrap(c("species"), scales="free_y")
```

@@

So, to modify run_truth we need to add the annage output but not replace the regular output in case users want output from non-age structured groups (inverts, etc.). Also need to see if lengths can be generaged from the annage outputs, if not need to keep the full set of outputs from the .nc file for all species to generate them.

Looks like the annagecatch output is only numbers and not weights.
